---
title: "IGUB-long analysis"
output: html_notebook
---
analysis of the two-part information gain and uncertainty in belief project, asking whether uncertainty in preschooler's intuitive theories in different domains drive explanation (information) seeking.

```{r}
rm(list = ls(all = TRUE))
#load needed libraries
library(psych)
library(gdata)
library(data.table)
library(ggplot2)

mydata  = read.table(file = "/Users/jennywang/Google Drive/cocodev/IGUB/IGUB_long_data.csv", sep=",",header=TRUE, na.strings="")
mydata[,c(23:34)] = as.numeric(mydata[,c(23:34)]=="y")
mydata$totalyes = rowMeans(mydata[,c(23:34)])

mydata=subset(mydata,mydata$yesnobias==0)

colnames(mydata)[1]<- "SubID"

```
```{r}
###overall descriptives
mydata$ToM=as.numeric(mydata$ToM=='table')
mydata$Germ=as.numeric(mydata$Germ=='temp')
mydata$Psycho=as.numeric(mydata$Psycho=='phone(tummy)')

des_m = describeBy(mydata,group=NULL,na.rm=TRUE)
```

```{r}
cor(mydata$ToM,mydata$ToM_ass_T)
cor(mydata$Germ,mydata$Germ_ass_T)
cor(mydata$Psycho,mydata$Psych_ass_T)
```

```{r}
#plot(mydata$ToM_ass_T,mydata$ToM)
```

```{r}
#SRCD analysis did median-split for ToM and Germ, and >1 for Psychosomatic
mydata$ToMf = as.factor(mydata$ToM_ass_T>=median(mydata$ToM_ass_T))
mydata$Germf = as.factor(mydata$Germ_ass_T>=median(mydata$Germ_ass_T))
mydata$Psychf = as.factor(mydata$Psych_ass_T>=median(mydata$Psych_ass_T))
# # 
# mydata$ToMf = as.factor(mydata$ToM_ass_T>=2)
# mydata$Germf = as.factor(mydata$Germ_ass_T>=2)
mydata$Psychff = as.factor(mydata$Psych_ass_T>=2)
mydata$Agef = as.factor(mydata$Age>=median(mydata$Age))


```

```{r}
des_T = describeBy(mydata$ToM,group=mydata$ToMf,na.rm=TRUE,mat=TRUE)
des_G = describeBy(mydata$Germ,group=mydata$Germf,na.rm=TRUE,mat=TRUE)
des_P = describeBy(mydata$Psycho,group=mydata$Psychf,na.rm=TRUE,mat=TRUE)
des_all=rbind(des_T,des_G,des_P)
des_all$item=c("ToM","ToM","Germ","Germ","Psych","Psych")
levels(des_all$group1)[levels(des_all$group1)=="FALSE"]<-"Lower"
levels(des_all$group1)[levels(des_all$group1)=="TRUE"]<-"Higher"

```

```{r}
ggplot(data=des_all,aes(x=item,y=mean,fill=group1))+
  geom_bar(stat="identity",position=position_dodge())+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),width=.1,
                position=position_dodge(.9))+
  ylim(0,1)+
  theme_bw()
```

```{r}
#ToM
temp.count = mydata[,c("ToM","ToMf")]
temp.table = table(temp.count)
temp.chisq = cbind(chisq.test(temp.table)$statistic,chisq.test(temp.table)$p.value)
temp.table
chisq.test(temp.table,simulate.p.value=TRUE,B=2000)
chisq.test(temp.table)

```

```{r}
#Germ
temp.count = mydata[,c("Germ","Germf")]
temp.table = table(temp.count)
temp.chisq = cbind(chisq.test(temp.table)$statistic,chisq.test(temp.table)$p.value)
temp.table

chisq.test(temp.table,simulate.p.value=TRUE,B=2000)
chisq.test(temp.table)

```

```{r}
#Psychosomatic super low vs. higher
temp.count = mydata[,c("Psycho","Psychff")]
temp.table = table(temp.count)
temp.chisq = cbind(chisq.test(temp.table)$statistic,chisq.test(temp.table)$p.value)
temp.table

binom.test(11,13,0.5)
chisq.test(temp.table[,1])

chisq.test(temp.table,simulate.p.value=TRUE,B=2000)
chisq.test(temp.table)

```

```{r}
#combine Germ and ToM
temp.table=table(mydata[,c("Germ","Germf")])+table(mydata[,c("ToM","ToMf")])
temp.table
chisq.test(temp.table,simulate.p.value=TRUE,B=2000)
chisq.test(temp.table)

```

```{r}
#linear model for combining Germ and ToM
cdata <- mydata[,c("SubID","ToM","ToMf")]
summary(aov(ToM~ToMf,data=cdata))

cdata <- mydata[,c("SubID","Germ","Germf")]
summary(aov(Germ~Germf,data=cdata))

#cdata<-melt(cdata,id=c("SubID","ToMf"))
#summary(aov(value~ToMf*variable+Error(SubID),data=cdata))
```

```{r}
#combine 3 domains
temp.table=table(mydata[,c("ToM","ToMf")])+table(mydata[,c("Germ","Germf")])+table(mydata[,c("Psycho","Psychf")])
temp.table
chisq.test(temp.table,simulate.p.value=TRUE,B=2000)
chisq.test(temp.table)

#is low-performers preferring, or is high-performers ignoring?
binom.test(43,64,0.5)
binom.test(42,86,0.5)

```

```{r}
#combine 3 domains analyze effect of age
temp.table=table(mydata[,c("ToM","Agef")])+table(mydata[,c("Germ","Agef")])+table(mydata[,c("Psycho","Agef")])
temp.table
chisq.test(temp.table,simulate.p.value=TRUE,B=2000)
chisq.test(temp.table)

```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

